Model

### 2019-09-18 stats/model.Rmd
update model file

data_comb_log

@@

var all_log_likes = map(function(row) { 
      var prior = [row.prior, 1-row.prior]
        var itemLineParameters = all_item_parameters[row.item]
        var sem_knowledge = logistic(itemLineParameters.intercept + 
            itemLineParameters.slope * row.age)
        var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age

        var modelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)

        return modelPredictions.score(row.correct)

    //  query.add(["prediction", item, row.age, row.alignment], ["NA", Math.exp(modelPredictions.score(1))])
  // return loglike
   }, dataFromR.comb_data)

  var log_likelihood = sum(all_log_likes)
  query.add(["log_like", "NA", "NA"], ["NA", log_likelihood])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 100000,
                        burn = 50000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

#saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_log_like.rds")

@@

log_like<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -item, -age, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
  group_by(Chain)%>%
  summarize(logP = logSumExp(log_like))

## Flat prior model

```{r work in progress}
flat_prior <- '
var data = dataFromR.data

var all_log_likes = map(function(row) { 
      var prior = [row.prior, 1-row.prior]
        var itemLineParameters = all_item_parameters[row.item]
        var sem_knowledge = logistic(itemLineParameters.intercept + 
            itemLineParameters.slope * row.age)
        var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age

        var modelPredictions = pragmaticListener({label: "novel_word"}, [.5,.5], speakerOptimality, sem_knowledge)

    //    display(modelPredictions.score(row.correct))

        return modelPredictions.score(row.correct)

    //  query.add(["prediction", item, row.age, row.alignment], ["NA", Math.exp(modelPredictions.score(1))])
  // return loglike
   }, dataFromR.comb_data)

  var log_likelihood = sum(all_log_likes)
  query.add(["log_like", "NA", "NA"], ["NA", log_likelihood])

sem_know_model_flat_prior<- webppl(
  program_code = paste(rsaUtils, rsaModel, flat_prior , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 100000,
                        burn = 50000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

saveRDS(sem_know_model_flat_prior, "../saves/sem_know_model_variant3_100k_flat_prior_log_like.rds")

model_pred<- sem_know_model_flat_prior %>%
  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
  filter(parameter == "prediction")%>%
  separate(value, into = c("na", "me_effect"),sep = ",")%>%
  select(-na)%>%
  mutate(age = as.numeric(age),
         me_effect =as.numeric(str_remove(me_effect,"[)]")))

log_like_flat_prior<- sem_know_model_flat_prior %>%
  separate(Parameter, into = c("parameter", "item","age","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -item, -age, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
  group_by(Chain)%>%
  summarize(logP = logSumExp(log_like))

>>>>

data_comb_log
```

@@

var all_log_likes = map(function(row) { 
  var prior = [row.prior, 1-row.prior]
  var itemLineParameters = all_item_parameters[row.item]
  var sem_knowledge = logistic(itemLineParameters.intercept + 
                               itemLineParameters.slope * row.age)

  var global_sem_knowledge = logistic(globalLineParameters.intercept + 
                               globalLineParameters.slope * row.age)

  var speakerOptimality = speakerOptimalityParameters.intercept  + 
      speakerOptimalityParameters.slope * row.age

  var pragModelPredictions = pragmaticListener({label: "novel_word"}, 
                                               prior, speakerOptimality, 
                                               sem_knowledge)

  var globalPragModelPredictions = pragmaticListener({label: "novel_word"}, 
                                               prior, speakerOptimality, 
                                               global_sem_knowledge)

  var flatModelPredictions = pragmaticListener({label: "novel_word"}, 
                                               [.5, .5], speakerOptimality, 
                                               sem_knowledge)

  return {
    prag: pragModelPredictions.score(row.correct),
    globalPrag: globalPragModelPredictions.score(row.correct),
    flat: flatModelPredictions.score(row.correct),
    priorOnly: Math.log(row.correct == 1 ? row.prior : 1 - row.prior)
  }

}, dataFromR.comb_data)

var log_likelihood_prag = sum(_.map(all_log_likes, "prag"))
var log_likelihood_prag_global = sum(_.map(all_log_likes, "globalPrag"))
var log_likelihood_flat = sum(_.map(all_log_likes, "flat"))
var log_likelihood_prior_only = sum(_.map(all_log_likes, "priorOnly"))

query.add(["log_like", "pragmatics", "NA"], ["NA", log_likelihood_prag])
query.add(["log_like", "pragmatics_global", "NA"], ["NA", log_likelihood_prag_global])
query.add(["log_like", "flat_prior", "NA"], ["NA", log_likelihood_flat])
query.add(["log_like", "prior_only", "NA"], ["NA", log_likelihood_prior_only])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH",
                        samples = 100000,
                        burn = 50000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 5000)
)

saveRDS(sem_know_model, "../saves/sem_know_model_variant3_100k_model_comparison.rds")

@@

log_like<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "model","age","alignment"), sep = ",")%>%
  filter(parameter == "log_like")%>%
  separate(value, into = c("na", "log_like"),sep = ",")%>%
  select(-na, -age, -alignment)%>%
  mutate(log_like =as.numeric(str_remove(log_like,"[)]")))%>%
  group_by(model, Chain)%>%
  summarize(logP = logSumExp(log_like))
